---
title: "Project 1 Asuransi Umum dan Kerugian"
author: "Maulida Nur Shabrina"
output:
  html_document:
    df_print: paged
---

---
		For this project, we will use a set of claim data called \{autoinsurance.csv }. The main goal of this test is to compute the relativities for the premium based on a set of rating factors. Statistical tests will be performed to measure the quality of the fit and determine whether the given rating factors are statistically significant to predict the frequency and/or severity component ofthe tariff model. All statistical tests should be performed at a confidence level of 95\%.
	
########## Question 1
Briefly discuss the data found (e.g., how many tariff cells, how many rating factors, what are the levels for each, how is the exposure determined).

Answer:
a. There are 4 rating factors, including: zone, vehicle, age, and bonus
b. Levels: - zone   : 4 level
           - vehicle: 3 level
           - age    : 4 level
           - bonus  : 3 level
c. Tarrif cells : (4)(3)(4)(3) = 144, there are 144 tarrif cells
d. Exposure: duration as frequency and nbclaim as severity.

Rcode:
```{r}
library(foreach)
library(ggplot2)
library(MASS)
library(dplyr)
library(tinytex)
library(rmarkdown)
```

## Import data
```{r}
data = read.delim("autoinsurance.csv", sep=",")
head(data)
```

```{r}
summary(data)
```


## Converting predictor variables into categorical variables
```{r}
data <- within(data, {
  zone <- factor(zone)
  vehicle <- factor(vehicle)
  age <- factor(age)
  bonus <- factor(bonus)
})
summary(data)
```
## Calculating the outcomes/categories that differ for each predictor
```{r}
levels(data$zone)
```


```{r}
levels(data$vehicle)
```


```{r}
levels(data$age)
```


```{r}
levels(data$bonus)
```
From the level function, it is known that the predictors zone and age have 4 different categories, while vehicle and bonus have 3 categories each.

## Tariff Cells
```{r}
length(levels(data$zone))*length(levels(data$vehicle))*length(levels(data$age))*length(levels(data$bonus))
```
There are 144 Tariff cells

## Defining frequency and severity
```{r}
# defining frequency
frequency = data$nbclaim/data$duration
head(frequency)

# defining severity
n = 144
severity = 0
for(i in 1:n){
  if(data$nbclaim[i] == 0){severity[i] = 0}
  else{severity[i] = data$totalclaim[i]/ data$nbclaim[i]}
}
head(severity)

# Combining frequency and severity into one dataframe 
data2 <- cbind(data,frequency, severity)
head(data2)
```

########## Question 2
We first focus on the frequency component of the tariff model. An insurer's current tariff uses the categorical variables Zone, Vehicle, Age, and Bonus as predictors. Using a relative Poisson glm (with a base tariff cell set as the tariff cell with the largest exposure as measured by the variable Insured), produce a table with the relativity for each predictor in the model, as well as a $95\%$ confidence interval for each relativity. Comment on the significance of each predictor in the model. Also, using the deviance statistic, discuss the overall fit of this model to the 

Answer: 
Based on the tariff cell with the largest exposure, the tariff cell (3, 3, 4, 3) is designated as the base tariff cell. Additionally, it can be observed that nearly all rating vectors have a p-value < alpha = 0.05, indicating that the rating vectors are significant to the model.

However, for the rating vectors zone4 and bonus2, the p-value is > alpha = 0.05, indicating that the rating vectors zone4 and bonus2 are not significant to the model.

It can also be noted that the scaled deviance is 132.1301, which is less than the critical value of 160.9148. The same result can also be seen from the p-value of 0.505003 > alpha = 0.05. Thus, it can be concluded that the frequency fitting model with relative Poisson provides good results.

Rcode: 
## To better understand the relationship between predictors and claim frequency
```{r}
# frequency vs zone
plot(data2$zone, data2$frequency, col="red",xlab="zone",ylab="claim frequency")
```


```{r}
# frequency vs vehicle
plot(data2$vehicle, data2$frequency, col="red",xlab="vehicle",ylab="claim frequency")
```


```{r}
# frequency vs age
plot(data2$age, data2$frequency, col="red",xlab="age",ylab="claim frequency")
```

```{r}
# frequency vs bonus
plot(data2$bonus, data2$frequency, col="red", xlab="bonus", ylab="claim frequency")

```
From the boxplot, it can be observed that many data points on the graph are above the boxplot. This occurs because the majority of the data have values of 0, causing the quartile values and the mean to be below the majority of the provided data.

## GLM Fitting
```{r}
# Setting the maximum exposure as the base tariff.
print(basecell<- data2[which.max(data2$duration), 1:4 ])
```


```{r}
print(data2$zone<- relevel(data2$zone, as.character(basecell$zone)))
```


```{r}
print(data2$vehicle<- relevel(data2$vehicle, as.character(basecell$vehicle)))
```


```{r}
print(data2$age<- relevel(data2$age, as.character(basecell$age)))
```


```{r}
print(data2$bonus<- relevel(data2$bonus, as.character(basecell$bonus)))
```
We pick tariff cell (3, 3, 4, 3) to be the base tariff cell
 
 
##  Fit relative Poisson glm (with phi=1) for number of claims that uses an offset
```{r}
summary(model.frequency <- glm(nbclaim ~ zone + vehicle + age + bonus + offset(log(duration)), data = data2[data2$duration>0, ], family = poisson("log")))

```
## Deviance
```{r}
cbind(scaled.deviance=model.frequency$deviance,df=model.frequency$df.residual, p=1-pchisq(model.frequency$deviance, model.frequency$df.residual))

```
## Critical value of the test at 95% confidence level
```{r}
qchisq(0.95, 133)
```
From the above results, it is known that the scaled deviance is 132.1301, which is less than the critical value of 160.9148. The same result can also be observed from the p-value of 0.505003 > alpha = 0.05. Therefore, it can be concluded that the fitting model with relative Poisson provides good results.

```{r}
# Update model.frequency model, dropping zone variable
summary(model.frequency2 <- glm(nbclaim ~ vehicle + age + bonus + offset(log(duration)), data = data2[data2
$duration>0,], family = poisson))

```
```{r}
anova(model.frequency2,model.frequency,test = "Chisq")
```
Hypothesis Test
H0: all betas of the zone variables equal 0
H1: at least one beta of the zone variables does not equal 0

Significance Level
α = .05

Critical Region
H0 is rejected if p-value < 0.05

Test Statistic
p-value < 2.2e-16

Interpretation
From the calculation results, it is found that the p-value < 2.2e-16 < α = 0.05, thus H0 is not rejected. It can be concluded that the full model is better than removing the zone predictor from the model.

```{r}
# Update model.frequency model, dropping bonus variable
summary(model.frequency3 <- glm(nbclaim ~ zone + vehicle + age +  offset(log(duration)), data = data2[data2
$duration>0,], family = poisson))


```

```{r}
anova(model.frequency3,model.frequency,test = "Chisq")
```
Hypothesis Test
H0: all betas of the bonus variables equal 0
H1: at least one beta of the bonus variables does not equal 0

Significance Level
α = .05

Critical Region
H0 is rejected if p-value < 0.05

Test Statistic
p-value = 2.06e-08

Interpretation
From the calculation results, it is found that the p-value = 2.06e-08 < α = 0.05, thus H0 is not rejected. It can be concluded that the full model is better than removing the bonus predictor from the model. Therefore, the full model will be retained.


## Constructing Relativities Table
```{r}
z.alpha=qnorm(0.975)
exp.beta=exp(model.frequency$coefficients)
exp.lower.bound=exp(model.frequency$coefficients-z.alpha*sqrt(diag(vcov(model.frequency))))
exp.upper.bound=exp(model.frequency$coefficients+z.alpha*sqrt(diag(vcov(model.frequency))))
relativity.table=cbind(exp.beta,exp.lower.bound,exp.upper.bound)
relativity.table
```

########## Question 3
We now turn our attention to the severity model. Fit a Gamma glm (with log link function) using all categorical variables. Comment on the significance of each predictor in the model. Also,using the deviance statistic, discuss the overall fit of this model to the data.

Answer: Based on the results from modeling severity using all categorical variables, it is found that the intercept and predictor variables zone1, vehicle1, vehicle2, and age2 have p-values < alpha = 0.05, indicating that these variables significantly influence the model.

From the computations, it is also found that the predictor variables zone2, zone4, age1, age3, bonus1, and bonus2 have p-values > alpha = 0.05, indicating that these predictor variables do not significantly influence the model.

Additionally, it is observed that the scaled deviance is 95.16695, which is less than the critical value of 123.2252. The same result is reflected in the p-value of 0.5903498 > alpha = 0.05. Thus, it can be concluded that the severity fitting model with gamma GLM fit is considered to provide a good fit to the data.


# Fits a gamma glm on claim severity, using only the classes that have more than one claim
```{r}
summary(model.severity <- glm(severity ~ zone + vehicle + age + bonus, data = data2[data2$nbclaim > 0, ], family = Gamma("log"), weights = nbclaim))

```
## The dispersion parameter phi
```{r}
print(dispersion<-summary(model.severity)$dispersion)
```
## Deviance
```{r}
scaledtest<-with(model.severity, cbind(res.deviance = model.severity$deviance/dispersion, df = model.severity$df.residual, p = 1-pchisq(model.severity$deviance/dispersion, df.residual)))

scaledtest
```

```{r}
qchisq(0.95, 99)
```
The scaled deviance is 95.16695, which is less than the critical value of 123.2252. The same conclusion can be drawn from the p-value of 0.5903498, which is greater than alpha = 0.05. Therefore, it can be concluded that the severity fitting model with gamma GLM fit is considered to provide a good fit to the data.

########## Question 4
Consider the claim severity model, if your manager ask your suggestion for simplifying the model (you can merge rating factors or deleted rating factors), what is your suggestion? Statistically justify your answer.

Answer: Based on the computation results, it is statistically justified to simplify the claim severity model by removing the predictor variable "bonus" from the model because the model has a p-value of 0.1915, which is greater than alpha = 0.05. Therefore, the model is better without the "bonus" variable compared to the full model.

```{r}
## Update model.severity model, dropping zone variable
model.s1 <- update(model.severity, . ~ . - zone)
model.s1
```

```{r}
## test model differences with chi square test
anova(model.s1, model.severity, test = "Chisq")
```
The p-value is 0.03308, which is less than 0.05, indicating that the model is not better if the "zone" variable is removed.

```{r}
## Update model.severity model, dropping age variable
model.s2 <- update(model.severity, . ~ . - age)
model.s2

```
```{r}
## test model differences with chi square test
anova(model.s2, model.severity, test = "Chisq")
```
The p-value is 0.01365, which is less than 0.05, indicating that the model is not better if the "age" variable is removed.

```{r}
## Update model.severity model, dropping bonus variable
model.s3 <- update(model.severity, . ~ . - bonus)
model.s3

```
```{r}
ms3 = summary(model.severity3 <- glm(severity ~ zone + vehicle + age , data = data2[data2$nbclaim > 0, ], family = Gamma("log"), weights = nbclaim))
```


```{r}
## test model differences with chi square test
anova(model.s3, model.severity, test = "Chisq")
```
The p-value is 0.1915, which is greater than alpha = 0.05, indicating that the model is better if the "bonus" variable is removed. Therefore, it is statistically justified to simplify the model by removing the predictor variable "bonus".

In the end, the model used is the one with the "bonus" variable removed.

### Constructing relativities table
```{r}
z.alpha=qnorm(0.975)

exp.beta2 = exp(model.s3$coefficients)

exp.lower.bound2 = exp(model.severity3$coefficients-qt(0.975,ms3$df.residual)*sqrt(diag(ms3$cov.scaled)))

exp.upper.bound2 = exp(model.severity3$coefficients+qt(0.975,ms3$df.residual)*sqrt(diag(ms3$cov.scaled)))


relativity.table2=cbind(exp.beta2,exp.lower.bound2,exp.upper.bound2)
relativity.table2

```


########## Question 5
Find the expected pure premium (for a coverage of a full policy year) of a policy with Zone=2, vehicle=3, age=4, and bonus=1.

Answer: The pure premium for a policy with Zone = 2, vehicle = 3, age = 4, and bonus = 1 is 31.60204.

Rcode:
## Pure premium for the frequency
```{r}
relativity.table[1,1]*relativity.table[3,1]*relativity.table[10,1]

```
## Pure premium for the severity
```{r}
relativity.table2[1,1]*relativity.table2[3,1]

```
## Thus, the pure premium is  
```{r}
relativity.table[1,1]*relativity.table[3,1]*relativity.table[10,1]*relativity.table2[1,1]*relativity.table2[3,1]
```

########## Question 6
Suppose that there are 500 independent 1-year policy in the tariff cell with Zone=2, vehicle=3, age=4, and bonus=1. Find the probability that this group of policyholder generate more than 3 claims in total?

Answer: The probability that this group of policyholders will have more than 3 claims in total is 0.05664714.

Rcode:
# Number of claims per policy in tariff cell is poisson distributed with mean
```{r}
relativity.table[1,1]*relativity.table[3,1]*relativity.table[10,1]
```
# Thus, for 500 independent 1-year policies within the tariff cell, the total number of claims is also distributed Poisson with a mean of
```{r}
500*relativity.table[1,1]*relativity.table[3,1]*relativity.table[10,1]
```
# The probability that this group of policyholders will generate more than 3 claims is
```{r}
1-ppois(3,500*relativity.table[1,1]*relativity.table[3,1]*relativity.table[10,1])
```